---
name: Chris
surname: Mantegna
position: "PhD Student"
pronouns: she/her
address: "School of Aquatic and Fishery Sciences, University of Washington"
phone: 206.823.4242
www: github.com/ChrisMantegna
email: "mantegna@uw.edu"
twitter: marinemantegna
github: ChrisMantegna
linkedin: ChrisMantegna
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Summary 

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
  "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
  "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Peer Reviewed Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

# Other Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

# Grants

# Research Impacts and Merit

# Awards

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>%
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year,
    Desc
  )
```

# Invited Lectures and Presentations

# Contributed Conference Presentations

# Teaching Mentoring & Engagement
Courses Taught
Course Guest Lecture
Professional Development Trainings
Students Advised
Other Mentoring
Engagement Activities
Service Activities (UW facing)
Professional Affiliations
